Improvement of crash forces in structures using optimization tools.

### 2016-07-27 paper.tex
Avances

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed (see \Cref{fig:general}. In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. The trigger starts a desired collapse mode in that area.

@@

Due to the crushing conditions and the relation between tube length and cross section area, strong difficulties were found in order to achieve stable collapse mechanisms. On their place, tubes diverted from their axis ---other found problems not related with the tube bending are solved through the use of rivets---. Trying to avoid these critical situations, four rigid plates on a rectangular section among the crash tube were added to the model as a stabilizing box.

It has half of the length of the tube and moved together with the impact plate, so the crash tube would end confined between the plates on both ends and the stabilizing box by the end of the simulation. Its section was of $\num{100}\times\SI{60}{\mm}$ and co-centered with the crash box.

>>>>

The tube is crushed between two rigid plates, one fixed and the other moving at impact speed (see \Cref{fig:general}). In order to ease the formation of a stable collapse mechanism, a triggering is machined near the front end of the tube. The trigger starts a desired collapse mode in that area. Due to the high slenderness of the tube, difficulties were found in order to achieve stable collapse mechanisms. On their place, tubes diverted from their axis. Trying to avoid these critical situations, four rigid plates on a rectangular section around the crash tube were added to the model as a bounding box. Its section was $\num{100}\times\SI{60}{\mm}$ and co-centered with the crash box.

@@

It has half of the length of the tube and moved together with the impact plate, so the crash tube would end confined between the plates on both ends and the stabilizing box by the end of the simulation.
